---
title: "R @ MMC"
subtitle: "Costas T Lambrew Research Retreat \n"
date: "May 1, 2019"
output:
  revealjs::revealjs_presentation:
    theme: blood
    highlight: zenburn
    center: TRUE
    transition: fade
    reveal_options:
      slideNumber: TRUE
      autoSlide: 25000
      loop: TRUE
      autoPlayMedia: TRUE
---
##  Visualize your data
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(gtsummary)
library(dplyr)
htmltools::img(src = knitr::image_uri("images/animated.gif"), 
               alt = 'plots', 
               style = 'background:none; border:none; box-shadow:none; position:relative;')
```


## Create maps!
```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri("images/animated_map.gif"), 
               alt = 'map', 
               style = 'background:none; border:none; box-shadow:none; position:relative;')
```


## Statistics and machine learning
```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri("images/islr_graph.jpg"), 
               alt = 'islr', 
               style = 'background:none; border:none; box-shadow:none; position:relative;')
```


## Programmatically generate tables
```{r}
tbl_summary(trial[c("trt", "age", "grade", "response")], 
            by = "trt") %>%
  add_comparison() 
```





## **MMC R server** 
### Access your work from any MaineHealth computer with a web browser
**[https://vmrstudiowebap](https://vmrstudiowebap)**


## **MMC R server** 
### Install packages with ease

```{r eval=FALSE, tidy=FALSE}
install.packages("tidyverse")
```


## **MMC R server** 
### Use Python
```{python}
import pandas as pd
my_series = pd.Series([2, 4, 6, 8, 10])
print(my_series.describe())
```


## **MMC R server** 
### Connect to databases
```{r, eval=FALSE}
con <- dbConnect(odbc(), Driver = "{ODBC Driver 17 for SQL Server}", 
    Server = "localhost", 
    Database = "testdb", 
    UID = "SA", 
    PWD = rstudioapi::askForPassword("Database password"), 
    Port = 1433)
```


## **MMC R user group**
- Get help from peers
- Meets first Tuesday of every month at CORE
- Upcoming topics
    + Programmatic tables (**Next Tuesday**)
    + Baysian multilevel modeling
    + Causal inference and Structural Equation Modeling
    + Big data

## Data Carpentry Workshop at Core
```{r echo = FALSE, message=FALSE}
library("htmltools")
library("vembedr")
embed_url("https://youtu.be/yK2vexb2QEI")
```